Supplementary Materials from: \textit{Innovation and elaboration on the avian tree of life}; Science Advances, in review

### 2023-06-09 Manuscript/supplementaries.tex
fixed typo in Zoe's name
Final bits resubmitted

\author{Thomas Guillerme, 
Jen A. Bright,
Christopher R. Cooney\\
Emma C. Hughes,
Zoe K. Varley,
Natalie Cooper,
Andrew P. Beckerman,\\
and Gavin H. Thomas}

@@

With $$\vec{species}_{x}$$ being the vector in $n$ dimensional space for species $x$. And $$\textbf{v}_{clade}$$ being the eigen vector of a specific clade (e.g. $$\textbf{v}_{clade_{c}}$$)

>>>>

\author{Thomas Guillerme, 
Jen A. Bright,
Christopher R. Cooney\\
Emma C. Hughes,
Zo\"{e} K. Varley,
Natalie Cooper,
Andrew P. Beckerman,\\
and Gavin H. Thomas}

@@

With $\vec{species}_{x}$ being the vector in $n$ dimensional space for species $x$. And $\textbf{v}_{clade}$ being the eigen vector of a specific clade (e.g. $\textbf{v}_{clade_{c}}$)
